### 2015-01-16 fundamentals/examples.tex
simpler sentence

The \Cyclus community-driven software development model seeks to break the 
unproductive proliferation of overspecialized simulators and instead leverages 
the collective expertise of fuel cycle researchers toward a single, more 
extensible, tool. Through the targeted
contributions of those researchers, an ecosystem of capabilities should emerge.
The \Cyclus `Ecosystem' is the collection of tools, calculation libraries, 
archetypes, data, and input files intended for use with the \Cyclus simulator. 
Members of the ecosystem include:
\begin{itemize}
\item the archetypes provided in the \Cycamore \cite{carlsen_cycamore_2014} 
repository
\item the archetypes created by researchers
\item isotopic composition data
\item historical facility deployment data
\item the \Cyclus \gls{GUI} tool Cyclist
\item fundamental analysis tools in the \Cyclus toolkit
\item tools for \Cyclus optimization, parallelization, and development
\end{itemize}
Taken together, these form an ecosystem of capabilities. Over time, this 
ecosystem will grow as archetype developers, kernel developers, and 
even users contribute capabilities developed for their own needs. Indeed, the 
long-term vision for the \Cyclus framework predicts an ever-expanding ecosystem 
of both general and specialized capability extensions.

>>>>

The \Cyclus community-driven software development model seeks to break the 
unproductive proliferation of overspecialized simulators. It instead leverages 
the collective expertise of fuel cycle researchers toward a single, more 
extensible, tool. Through the targeted
contributions of those researchers, an ecosystem of capabilities should emerge.
The \Cyclus `Ecosystem' is the collection of tools, calculation libraries, 
archetypes, data, and input files intended for use with the \Cyclus simulator. 
Members of the ecosystem include:
\begin{itemize}
\item the archetypes provided in the \Cycamore \cite{carlsen_cycamore_2014} 
repository
\item the archetypes created by researchers
\item isotopic composition data
\item historical facility deployment data
\item the \Cyclus \gls{GUI} tool Cyclist
\item fundamental analysis tools in the \Cyclus toolkit
\item tools for \Cyclus optimization, parallelization, and development
\end{itemize}
Taken together, these form an ecosystem of capabilities. Over time, this 
ecosystem will grow as archetype developers, kernel developers, and 
even users contribute capabilities developed for their own needs. Indeed, the 
long-term vision for the \Cyclus framework predicts an ever-expanding ecosystem 
of both general and specialized capability extensions.
